Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
removed constant definitions that are not used, checked =:

%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing. Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{equation}
	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }
	\end{equation}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

% proposition b_2 to \infty
\begin{proposition}
	Assuming assumption \ref{assumption}, and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$,
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
	\begin{equation}
	   b_2 \eta_t^{b_2} \geq m_\eta.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

@@

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$. First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let 
	$$ \zeta_2 = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

	Next, consider $I_2^{b_2}$. Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
		\qquad \text{and} \qquad
		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
	\end{equation*}
	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
	\begin{IEEEeqnarray}{rCl}
		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\	
		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
	\label{eq:I2_b2_infty}
	\end{IEEEeqnarray}
	where $\kappa_3 = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.

@@

	% case 3: b1 to infinity
	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$. We have the following limits, for all $t \in [0,T)$:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 2+1= 3.$$

>>>>

%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing. Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{equation}
	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
	\end{equation}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

% proposition b_2 to \infty
\begin{proposition}
	Assuming assumption \ref{assumption}, and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$. Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
	$$ 
	and thus for all $t \in [0,T]$,
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}
	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
	\begin{equation}
	   b_2 \eta_t^{b_2} \geq m_\eta.
	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
	\end{equation}

@@

	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$. First, consider $I_1^{b_2}$. Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing. (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let 
	$$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\begin{array}{lclclclcl}
		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
	\end{array}
	\end{equation*}
	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
	$$
	Therefore,
	\begin{IEEEeqnarray}{rCl}
		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the last inequality comes from the definition of $\zeta_2$.

	Next, consider $I_2^{b_2}$. Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
		\qquad \text{and} \qquad
		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
	\end{equation*}
	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
	\begin{IEEEeqnarray}{rCl}
		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\	
		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
	\label{eq:I2_b2_infty}
	\end{IEEEeqnarray}
	where $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.

@@

	% case 3: b1 to infinity
	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. We have the following limits, for all $t \in [0,T)$:
	\begin{equation}
		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
	\label{eq:ut_wt_lim_b1_infty}
	\end{equation}
	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and
	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 2+1= 3.$$
